\documentclass[11pt, a4paper, sans]{moderncv}

\moderncvtheme[blue]{classic}
\moderncvcolor{CTUblue}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[tt=false]{libertine}
\usepackage[scale=0.88]{geometry}
\AtBeginDocument{\recomputelengths}

\firstname{Ondřej}
\familyname{Kvapil}
\title{Curriculum Vitae}
\email{viluon@pm.me}
\social[github]{viluon}
% \social[twitter]{real_viluon}
\homepage{viluon.me}

\begin{document}
\maketitle

\section{Education}
\cventry{2021--2023}{Master of Science}{Faculty of Information Technology,
Czech Technical University}{Prague, Czech Republic}{
\href{https://dspace.cvut.cz/handle/10467/108860}{P4 Language Server},
supervised by Ing. Viktor Puš, Ph.D., MBA}{}

\cventry{2017--2021}{Bc. in Computer Science}{Faculty of Information
Technology, Czech Technical University}{Prague, Czech
Republic}{\href{https://github.com/viluon/bachelors-thesis}{Haskell dynamic
tracing}, awarded
\href{https://fit.cvut.cz/cs/studium/pruvodce-studiem/bakalarske-a-magisterske-studium/cena-dekana}{dean's
award for outstanding final thesis}, supervised by Ing. Filip Křikava, Ph.D}{}

\cventry{2011--2017}{High school studies}{Gymnázium Olomouc-Hejčín}{Olomouc,
Czech Republic}{}{}

\subsection{Extracurricular activities}
\cvline{2018~--~present}{Organising the \href{https://fiks.fit.cvut.cz/}{FIKS}
correspondence competition to attract talented high school students to CTU
FIT.}

\cvline{2023}{Contestant at the \href{https://alignmentjam.com/jam/benchmarks}{
Safety Benchmarks Hackathon}.
\href{https://alignmentjam.com/project/exploring-the-robustness-of-model-graded-evaluations-of-language-models}{
Our project} won first place.}

\cvline{2023}{Attendee of the Programming Language Mentoring Workshop (PLMW)
at the ACM SIGPLAN Symposium on Principles of Programming Languages
(\href{https://popl23.sigplan.org/}{POPL 2023}), Boston, Massachusetts,
United States, January 15--21, 2023}

\cvline{2022}{Student of the Programming Language Implementation Summer School
(\href{https://pliss.org/2022/}{PLISS}), Bertinoro, Italy, October 24--29,
2022}

\cvline{2021}{Student of the School on Theoretical Informatics, Graphs And
Mathematical Applications
(\href{https://users.fit.cvut.cz/~vallatom/stigma/}{STIGMA}), Kruh u Jilemnice,
Czech Republic, September 13--17, 2021}

\cvline{2021}{Student of the Oregon Programming Languages Summer School
(Foundations of Programming and Security),
\href{https://www.cs.uoregon.edu/research/summerschool/summer21/participants.php}{online},
June 14--26, 2021}

\cvline{2021}{Student of the Programming Language Implementation Summer School,
\href{https://pliss.org/2021/}{online}, May 20 -- June 29, 2021}

\cvline{2020}{Student of the School on Theoretical Informatics, Graphs And
Mathematical Applications
(\href{https://users.fit.cvut.cz/~vallatom/stigma/}{STIGMA}), Kruh u Jilemnice,
Czech Republic, September 14--18, 2020}

\cvline{2019}{Student volunteer at \href{https://etaps.org/2019}{ETAPS}.}

\cvline{2019}{Contestant at Hack Kosice in Kosice, Slovakia.
\href{https://devpost.com/software/medify}{Our project} won the Efficient and
Faster Care Challenge.}

\cvline{2018}{Contestant at HackUPC 2018 in Barcelona, Spain.
\href{https://devpost.com/software/round-trip-flight-optimizer}{Our project}
won the Skyscanner Challenge.}

\cvline{2016--2017}{Participant in the \href{https://fiks.fit.cvut.cz/}{FIKS}
correspondence competition.}

\cvline{2012--2015}{Programmer in a high school team for the FIRST Lego League
robotics competition. 10th place in the FLL 2014 Central European finals in
Munich, out of more than 700 European teams.}

\cvline{2013}{Programmer in a high school team participating in the Volare
Space Robotics competition organised by the European Space Agency. We
\href{https://www.czechspace.cz/cs/druhe-misto-pro-rota}{placed second}
overall.}

\section{Experience}
\cventry{2022~--~present}{Compiler engineering
intern}{\href{https://intel.com/}{Intel}}{}{working on the
\href{https://github.com/p4lang/p4c}{P4 language compiler} in the Switching and
Fabric Group (XFG).}{}

\cventry{2021--2022}{Research
intern}{\href{https://prl-prg.github.io/}{Programming Research
Laboratory}}{}{developing dynamic analysis for Haskell programs to explore the
use of laziness in practice}{}

\cventry{2017--2019}{Java backend engineer}{Factorify}{}{worked on a web-based
ERP system designed for management and automation of factory workflows (Spring
framework, Nginx, PostgreSQL)}{}

\end{document}
